The Impact of Immutability on Class Size

### 2020-04-10 paper/article.tex
summaries
deep immutability

% \documentclass[a4paper,UKenglish,cleveref, autoref]{lipics-v2019}
\documentclass[12pt]{article}
\bibliographystyle{plainurl}
\title{The Impact of Immutability on Class Size}
\author{Yegor Bugayenko\\Huawei Technologies Co., Ltd.\\Russian Research Institute (RRI)\\\texttt{yegor.bugayenko@huawei.com}}{}{}
% \authorrunning{Yegor Bugayenko}
% \ccsdesc[100]{Software and its engineering~Object oriented languages}
% \keywords{Object-Oriented Programming, Immutability, NCSS}
\usepackage[utf8]{inputenc}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\input{../total}
\begin{document}
\raggedbottom
\maketitle

@@

Despite the existence of the \texttt{final} modifier, Reflection API enables
modification of any attributes in Java. Some mechanisms were suggested to
overcome this technical vulnerability, for example
via ``freezer'' objects~\cite{leino2008},
a new type system~\cite{tschantz2005},
or immutability assertion framework~\cite{pechtchanski2005}.
However, without any modifications to Java~\cite{steele2005},
thanks to the existence of Reflection API,
it's not possible to say whether a particular Java object is modified
after instantiation or not---any object can be modified.

@@

@@

\begin{figure}[h]
  \input{../ncss.tex}
  \caption{Distribution of class immutability by NCSS}
  \label{fig:1}
\end{figure}

>>>>

% \documentclass[a4paper,UKenglish,cleveref, autoref]{lipics-v2019}
\documentclass[12pt]{article}
\bibliographystyle{plainurl}
\title{The Impact of Immutability on Class Size}
\author{Yegor Bugayenko\\Huawei Technologies Co., Ltd.\\Russian Research Institute (RRI)\\\texttt{yegor.bugayenko@huawei.com}}{}{}
% \authorrunning{Yegor Bugayenko}
% \ccsdesc[100]{Software and its engineering~Object oriented languages}
% \keywords{Object-Oriented Programming, Immutability, NCSS}
\usepackage[utf8]{inputenc}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\input{total}
\begin{document}
\raggedbottom
\maketitle

@@

Despite the existence of the \texttt{final} modifier, Reflection API enables
modification of any attributes in Java. Some mechanisms were suggested to
overcome this technical vulnerability, for example
via ``freezer'' objects~\cite{leino2008},
a new type system~\cite{tschantz2005},
or immutability assertion framework~\cite{pechtchanski2005}.
However, without any modifications to Java~\cite{steele2005},
thanks to the existence of Reflection API,
it's not possible to say whether a particular Java object is modified
after instantiation or not---any object can be modified. As was noticed
by~\cite{hakonen1999} in relation to immutability,
``none of the current OO languages can prevent the programmer from writing
a piece of code which violates the integrity of an object''

@@

Even if programmers do not violate encapsulation via reflection, the
modified \texttt{final} only guarantees shallow immutability, as
explained by~\cite{hakonen1999}. Deep immutability, on the other hand,
exists only if the object pointed by the attributes are deeply immutable
(recursively).

@@

\begin{figure}[h]
  \input{ncss.tex}
  \caption{Distribution of class immutability by NCSS}
  \label{fig:1}
\end{figure}
